The DAO Hack

### 2019-01-04 paper/paper.tex
added some headings
adapted abstract

\paragraph{Abstract}
The DAO (decentralized autonomous organization) was an investment idea built on the ethereum blockchain. It was launched at the beginning of May 2016, had a lot of investors and raised a lot of money in ether.

Due to a security bug an unknown investor was able to retrieve a large portion of this investment in mid June 2016.

In this paper we will shortly explain what the DAO was meant to be and how it could be exploited. We will focus mostly on the security bug and the fallout.

@@

>>>>

\paragraph{Abstract}

In this paper we will explain what the DAO is, what happened to it and how the DAO could be exploited. We will give an overview of the security bug and on the fallout that followed.

@@

\section{What happened?}

\section{How was that possible?}

\section{What was the fallout?}
